\documentclass[12pt,oneside]{book}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{etoolbox}

\usepackage{xcolor}
\usepackage{times}

\usepackage{lastpage}
\renewcommand\bibname{ }
%\usepackage{mathptmx}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage[utf8]{inputenc}
\usepackage{fancyhdr}
 \pagestyle{fancy}
\fancyhf{}
%\lhead{Curriculum vitae}
\cfoot{ \hrule {\small Moslem Heidarpur}{\hfill\small Page \thepage ~of \pageref{LastPage}}}
 \usepackage{geometry}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=15mm,
 top=17mm,
 right=15mm,
  bottom=37mm,
 }
\setlength{\headsep}{0.2in} 
\setlength{\footskip}{0.5in} 

\newcommand{\fd}{\small \textit}
%\newcommand{\mtf}{ \fontfamily{put}\selectfont}
\newcommand{\mtf}{ \bf \normalsize}
\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

\usepackage[resetlabels]{multibib}
\bibliographystyle{ieeetr}
%\newcites{crypto}{{dff}} 
\definecolor{darkgreen}{rgb}{0,0.5,0}
\patchcmd{\thebibliography}{\chapter*}{\section*}{}{}
\renewcommand{\headrule}{{\color{gray}\hrule width\headwidth height\headrulewidth \vskip-\headrulewidth}}
\newcites{main,crypto}{{},{}}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=black,  % color of internal links
    urlcolor=blue    % color of external links
}


\newcommand{\position}{Assistant Professors in the Area of Computer Engineering }
\newcommand{\department}{in  Department of Electrical and Computer Engineering}
\newcommand{\university}{Concordia University}
\begin{document}\thispagestyle{empty}
\vspace*{-5em} \phantom \quad \\
\today\\
%\vspace*{0\baselineskip}\phantom \quad \\
Chair, Faculty Search Committee\\
\department ,\\
\university ,\\
2160 Bishop St suite 301 \\
Montreal, Quebec H3G 2E9\\
%\vspace*{2\baselineskip}
\phantom \quad \\
Dear Search Committee Members,\\

I am writing to express my interest in  the \position ~position   \department ~at \university . Currently employed as a Digital Logic Design Engineer at NXP Semiconductors, I am also a part-time research assistant in the Department of Electrical and Computer Engineering at the University of Windsor.

My research contributions have been in the area of neuromorphic engineering, Post-Quantum Cryptography (PQC) and Homomorphic Encryption (HE) circuit and systems.  
Throughout my MSc and PhD, I  have developed various novel techniques aimed at enhancing performance and reducing the area of systems implementing Spiking Neural Networks (SNNs), the third generation of neural networks. SNNs have numerous advantages over previous generations with wide range of applications  in classification and medical purposes.   

%As a postdoctoral fellow, I  started my research  on reducing  complexity and designing hardware for low-latency and low-area finite field  multipliers which are widely used in crytosystems.
%As a part time research assistant in University of Windsor, I am working on designing efficient hardware architecture to implement Post-Quantum Cryptography (PQC) and Homomorphic  Encryption (HE) systems, as these systems are becoming  hot research topics due to threat of  quantum computers and data privacy and security concerns.  

Subsequently, as a postdoctoral fellow, my focus shifted to reducing complexity and designing hardware for low-latency, low-area finite field multipliers widely used in cryptosystems.
In my role as a part-time research assistant at the University of Windsor, I am currently engaged in designing efficient hardware architectures for implementing PQC and HE systems. These areas have gained prominence due to the imminent threat of quantum computers and escalating concerns about data privacy and security.  My research contributions include several journal and conference papers, and two US patents. 


In my industry experience, I have actively participated in designing various System On Chips (SOCs), contributing to a team that designed an SOC utilizing artificial neural networks in cybersecurity. Presently, I am involved in the design of Ethernet controllers for integration into cars and other systems. These experiences have provided me with valuable insights into the requirements, development, and applications of embedded systems in the industry, and I am eager to bring this expertise into the research lab and classroom.

%
%During the time working in industry,  I was involved in designing various System On Chips (SOCs). I worked as a part of team which designed an SOC which used artificial neural networks in cybersecuirty. I am currently involved in designing Ethernet controllers to be  embedded in cars and other systems. During these times, I acquired genuine insight into the requirements, development and applications of embedded systems in industry. I intend to bring such experience into research lab and classroom.
 
Beyond my research activities, I have been fortunate enough to obtain wide range of teaching experiences. Since beginning  of my PhD, I have been involved in teaching and preparation of course materials in several courses including: Digital Logic Design, Embedded Systems and Electronics. 
As a postdoctoral fellow and part-time researcher at the University of Windsor, I provided guidance to PhD, MSc, and bachelor students. In my capacity as a seasonal instructor for continuing education, I conducted online courses in Cybersecurity.

Having been inspired by exceptional teachers and advisers, I recognize the profound impact a dedicated educator can have on a student. I am committed to following in their footsteps, continually improving my teaching and research skills.

 %Thank you for considering my application.
%
% I am also capable of teaching of the following courses with minimum or moderate preparation: Digital Logic Design, Embedded System Design, Digital Integrated Circuits Signals and Systems, Microprocessors, Digital Signal Processing, Electronics, Analog Integrated Circuit Design  etc. 
% My experience with outstanding teachers and advisers has made me realize
% how important one good teacher could be to a student. I tried to follow their path and work toward improving my teaching and research skills. 
\vspace*{1\baselineskip}
\phantom \quad \\
Sincerely,\\[0.2cm]
%\vspace*{1\baselineskip}
%\phantom \quad \\
Mason (Moslem) Heidarpur\\
217 Big Dipper St., Ottawa, ON, Canada, K4M 0J8\\
Email: heidarpur.m@gmail.com\\
Immigration status: Permanent resident of Canada\\[-0.1cm]
\newpage
\lhead{\textcolor{gray}{Curriculum vitae}}
\large \bf \hphantom \\ \\ 
 {\fontfamily{put}\selectfont Moslem Heidarpur} \mdseries \normalsize \\ \\ 
 \begin {itemize}
\item [] \phantom \quad  \item   []  {\bf  Webpages:} \vspace{-1.5em}
\item []  {\bf \hrulefill } \vspace{-1em}
\begin {itemize}
\item  \small \href{https://orcid.org/0000-0002-4116-0778 } {ORCID} 
%\item ORCID: \begin {itemize}  \item[] https://orcid.org/0000-0002-4116-0778 (\href{https://orcid.org/0000-0002-4116-0778 } {Hyperlink})  
%\end {itemize} 
%\item Google Scholar: \begin {itemize}  \item[] https://scholar.google.com/citations?user=bVzQEKkAAAAJ$\&$hl=en$\&$oi=ao  
\item \small \href{https://scholar.google.com/citations?user=bVzQEKkAAAAJ&hl=en&oi=ao  } { Google Scholar}
%\end {itemize}
%\item Linkedin:\begin {itemize}  \item[] https://www.linkedin.com/in/moslemheidarpur/ 
\item \small \href{https://www.linkedin.com/in/moslemheidarpur/   } {Linkedin}
 %\end {itemize}
%\item Researchgate:\begin {itemize}  \item[]  https://www.researchgate.net/profile/Moslem-Heidarpur 
\item \small \href{https://www.researchgate.net/profile/Moslem-Heidarpur/} {Researchgate}
% \end {itemize}
\end{itemize}  \vspace{0.5em}
\item  []  {\bf  Immigration status:}  \vspace{-1.5em}
\item []  {\bf \hrulefill } \vspace{-1em}
\begin {itemize} \item \small Permanent resident of Canada
\end {itemize}   \vspace{0.5em}
\item  [] {\bf  Address:} \vspace{-1.5em}
\item []  {\bf \hrulefill } \vspace{-1em}
\begin {itemize} 
\item  \small 217 Big Dipper, Ottawa, ON, Canada
\end{itemize}  \vspace{0.5em}
\item  []  {\bf  Email:} \vspace{-1.5em}
\item []  {\bf \hrulefill } \vspace{-1em}
\begin {itemize} 
 \item  \small heidarpur.m@gmail.com (preferred)
 \item \small heidarp@uwindsor.ca
 \item \small moslem.heidarpur@nxp.com
\end {itemize}   \vspace{0.5em}
\item  []   {\bf Phone:} \vspace{-1.5em}
\item []  {\bf \hrulefill } \vspace{-1em}
\begin {itemize} 
\item 6137976194
\end{itemize}
\end{itemize}

\newpage
\input{cvsections/education.tex} 
\newpage
\input{cvsections/research_exprience.tex}
\input{cvsections/researchinterests.tex}
\newpage
\input{cvsections/teaching_exprience.tex}
\newpage
\input{cvsections/work_exprience.tex}
\newpage
\input{cvsections/skills.tex}
\newpage
\input{cvsections/academic_services.tex}
\newpage
\input{cvsections/grants.tex}
\input{cvsections/awards.tex}
\input{cvsections/membership.tex}
\input{cvsections/presentations.tex}
\newpage
\input{cvsections/publications.tex}
%\input{cvsections/awards.tex}
\input{cvsections/references.tex}
%\input{research_proposal/sections/research_statement.tex}
\newpage
\input{research_proposal/sections/research_proposal_1.tex}
\newpage
 \input{research_proposal/sections/research_proposal_2.tex}
 %\newpage
 %\input{research_proposal/sections/research_proposal_3.tex}
 \input{teaching_dossier/cvsections/teaching_statement_v2.tex}
  \input{teaching_dossier/cvsections/teaching_interest.tex}
  \input{teaching_dossier/cvsections/teaching_exprience.tex}
    \input{teaching_dossier/cvsections/teaching_methodology.tex}
 \input{teaching_effectiveness/cvsections/teaching_effectiveness.tex}
 \input{diversity_statement/diversity_text.tex}


\end{document}
