
   \lhead{Teaching Methodology}
 \phantom \quad \\
   \newpage
    \thispagestyle{empty}
\hrule \phantom \quad  \vspace*{1\baselineskip}  \\
 {\bf Teaching Methodology}
 \vspace*{1\baselineskip}  \hrule \phantom \quad \\
\vspace*{3\baselineskip} \phantom \quad \\
 \mdseries \normalsize
As an enthusiastic educator, my teaching methodology centers on creating a dynamic and interactive learning environment that empowers students to actively participate in their educational journey. Through a combination of traditional and modern  approaches, I aim to cultivate critical thinking, communication skills, and a deep understanding of the subject matter.
\begin {itemize}
 \item  {\bf    Recorded Lecture}
        Engaging and informative lectures will form the foundation of the course, providing a comprehensive overview of key concepts and theories.
        Lectures would be enriched by utilizing multimedia resources, real-world examples, and case studies to enhance the learning experience. My plan is to record the lectures prior to the session ans share the video with with students.  This way, there would be more time during the class students would be involved by discussions, questions and group projects. 
\item  {\bf    Oral Questions by Teacher Answered Orally by Students:}
        I aim to actively ask questions to encourage students to understand the need to learn the topic and participate in discovering the solution to the problem that course address.  This approach promotes critical thinking, reinforcing key concepts and fostering a collaborative learning atmosphere.
 \item{\bf    Class Discussion Conducted by Teacher: }
        Facilitating lively class discussions to encourage students to express their opinions, ask questions, and engage in critical analysis.
        Incorporating diverse perspectives to enrich the learning experience and promote a deeper understanding of the subject matter.
\item { \bf    Presentations by Student Panels from the Class:}
        I am planning to incorporate student presentations in my courses, providing opportunities for them to develop research and communication skills. This approach not only encourages teamwork but also allows students to take ownership of their learning.
\item  {\bf   Reading Assignments in Academic Journals:}
        Assigning relevant readings from academic journals to deepen theoretical knowledge.
        Emphasizing the importance of staying current with scholarly literature and developing the ability to critically evaluate research.
\item{ \bf     Reading Assignments Related to Topic with Application in Industry: }
        I am planning to give reading assignment about application of course topics in the industry. The objective here is to explore real-world implications and connections between academic knowledge and industry practices.
\end {itemize}
In summary, by incorporating lectures, questions, discussions, student presentations, and a balance of academic and industry-related readings, I seek to equip students with a depp understanding of the subject, preparing them for success in both academic and professional pursuits.
