 \newpage \thispagestyle{empty}
 \lhead{Teaching Interests}
 \phantom \quad \\
\hrule \phantom \quad  \vspace*{1\baselineskip}  \\
 {\bf Teaching Interests}
 \vspace*{1\baselineskip}  \hrule \phantom \quad \\
\vspace*{3\baselineskip} \phantom \quad \\
In my previous teaching roles, I found great joy in breaking down complex ideas and creating an environment where students can comfortably engage with the material. These experiences have solidified my commitment to pursuing a long-term career in teaching.

My love for transferring knowledge aligns with my interest in developing course materials and teaching in areas such as digital logic design, computer architecture, embedded systems, system-on-chip, and microprocessor-based systems.
In particular, courses such as Introduction to Digital Systems, Introduction to Computer Organization and Architecture,  Computer Organization, Computer Systems Design,  Microprocessor Systems. Having taught courses like Computer Architecture and Digital Systems, and with industry experience focusing on embedded systems and logic design, I feel  prepared to offer a new perspective based on industry applications. 

I would enjoy teaching courses related to cybersecurity and cryptography as well. Currently, I teach Cybersecurity I and Cybersecurity II at the University of Windsor's Department of Continuing Education. These courses cover a range of topics, including social engineering hacking techniques, network attacks, data protection, secure protocols, cryptographic algorithms, authentication methods, and wireless network security. My research in cryptography, particularly in post-quantum algorithms and homomorphic encryption, further enriches my ability to provide relevant and up-to-date instruction.

The other topic that I am interested in teaching is artificial intelligence (AI), with a PhD thesis centered on AI and
% the attainment of a patent in the field 
 and published several research papers. I have also mentored MSc and PhD students in AI thesis and am eager to develop course materials for subjects such as Artificial Intelligence and Neural Networks, leveraging both my research and practical experiences.

Moreover, I have experience in networking as I worked as digital logic designer for a L2 switch for the past two years. I am interested in teaching Computer Networks courses that cover topics Networking Fundamentals, Routing and Switching, Basics of Transmission Systems an network architecture. I am also interested in teaching courses related to signal processing and  Digital Signal Processing. Furthermore, I have experience and interested  in teaching courses relate to electronics such electronics I and II and  digital electronics and cover topics transistors, diodes, op Amps, amplifier design, gate design , analysis power dissaption and delay. 

In summary,  I am eager to contribute to Carleton University through my diverse background and passion for education. My past teaching experiences, coupled with my  academic and research foundation as well as industry experience, put me in a good position to become dedicated  educator.











