\newpage
  \thispagestyle{empty}
 \lhead{ Diversity and Inclusion Statement}
 \phantom \quad \\
\hrule \phantom \quad  \vspace*{1\baselineskip}  \\
{\bf Diversity and Inclusion Statement}
 \vspace*{1\baselineskip}  \hrule \phantom \quad \\
\vspace*{3\baselineskip} \phantom \quad \\
 I am committed to create a welcoming environment in my classroom where everyone feels included. Diversity, to me, means embracing the different backgrounds and experiences that students bring. I believe each student have to feel valued and free to express themselves and  a diverse classroom is essential for preparing students to thrive in an interconnected world. 
 
 Diversity, extends far beyond demographics; it comprises of a range of identities and experiences, including race, ethnicity, gender, sexual orientation, socioeconomic background, disability, and cultural heritage. I am committed to acknowledging and celebrating diversity within my teaching and throughout the academic community.
 \begin{itemize}
\item{ Inclusive Teaching Practices:}
In my teaching, I employ inclusive practices that accommodate diverse learning styles and needs. I strive to create an environment where every student feels valued and heard. This involves employing a variety of instructional methods, offering diverse course content, and incorporating inclusive language.
\item{ Accommodations for Diverse Learning Styles:}
Recognizing that students have varied learning styles and needs, I am dedicated to providing accommodations that ensure equal access to educational opportunities. This may involve adapting materials, implementing flexible assessment methods, and leveraging technology to enhance accessibility.
\item{ Cultural Competence:}
I actively seek to enhance my cultural competence by engaging in ongoing education and self-reflection. I understand the importance of cultural sensitivity and strive to create an atmosphere that respects and appreciates diverse cultural perspectives.
 \item{ Creating a Welcoming Environment:}
I am dedicated to creating a welcoming and supportive environment for all students. My teaching philosophy emphasizes openness to diverse perspectives and a commitment to addressing any issues related to bias or discrimination in a proactive and constructive manner.
  \end{itemize}
 
My commitment to promoting diversity and inclusion in academia is grounded in my personal experience. During my PhD in Canada, I was fortunate to work alongside insightful faculty members in University of Windsor. I was truly inspired by their commitment to social justice, diversity and inclusion. 
%I became friends with people from  LGBTQ community.  Hearing their stories and experiences, and learning that some are still afraid to come out and be honest about their identity, reminded of my own experience as an ethnic minority. 
 %I truly admired them and hope that one day no one experience stigma and discrimination because of sexual orientation. 
  I have had the opportunity to address diversity and inclusion  in my roles as Graduate Assistant and Postdoctoral Fellow at University of Windsor. 
 I am committed to create an environment free from discrimination based on the race, religion, sex, economic status, sexual orientation, disability or other characteristics.
